Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Minor: broke long lines into new lines
Added paths to the figs folders in the repo and Dropbox folders

```{r}
# if the figs folder doesn't exist, create it for storing the figures
figs_dir <- "figs"

>>>>

```{r}
# if the figs folder doesn't exist, create it for storing the figures
gh_figs_dir <- "../figs/"
dropbox_figs_dir <- "~/Dropbox/My Academic Repository/Manuscripts/First author/In review/2022 - Systematic review of ORV models/Epidemics/submission2/manuscript_writeup/figs/"
